DTOADQ

### 2017-11-29 testdocs/_region_.tex
doicumentation

\message{ !name(test.tex)}\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=1.15in]{geometry}

@@

  	It seems that the GPU is not for me or DTOADQ and something I do not enjoy to use nor am good at. However, for this project, I had to deal with it. To overcome the lack of a random function, of which high quality uniform random generation is necessary for Monte Carlo simulations, I used the MWC64X algorithm. While there are better algorithms, they fail on branches which makes it useless for DTOADQ. It seemed to work well enough. The downside is that each worker/pixel needs its own random state, preserved across multiple kernel calls. There are indefinitely better solutions.
  \section{Light Transport Introduction}
  \section{Bidirectional Path Tracing}
    The main foundation of the mathematics and theory have come from many sources, from Veach's PhD thesis to PBR 3rd ed. and various open source path tracing kernels such as NanoRT, Embree, etc. However, the implementation differs from these in that the algorithm is optimized for the GPU. This section is about transforming the algorithms and mathematical models from Veach's thesis into something easily and efficiently implementable the GPU.

@@

  The rendering equation is:
  \begin{align}
    L_o(P, \omega_o) = L_e(P, \omega_o) + \int_{S}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) \vert cos\theta_i\vert d\omega_i
  \end{align}

  Where:
  	 $Lo(P,\:\omega_o)$ is the radiance at point $P$ in space towards direction $\omega_o$.

  	 $L_e(P,\:\omega_o)$ is the emittance at point $P$ towards $\omega_o$ (such as a lamp).

  	 $S$ is the unit sphere in which the angle $\omega_i$ is integrated over in respects to the normal at $P$. Also, this means, implicitly, that the equation is in respects to solid angle; the angle at which a primitive $A$ subtends $B$.

  	 $f_s$ is the Bidirectional Scattering Distribution Function. This will be detailed in the BSDF chapter, suffice it to say, it describes how photons are scattered (or absorbed) from point P in space from direction $\omega_i$ towards $\omega_o$ -- either through reflection (BRDF), or transmittance (BTDF). In volumetric path tracing, there is also subsurface scattering.

  	 $L_i(P, \omega_i)$ is the rendering equation at P from $\omega_i$

  	 And $cos\theta_i$ is the normal attenuation.

  Conceptually, this is the behavior of photons bouncing off several surfaces of a scene. While it's a very simple model, it's impossible to solve analytically for anything but the most simple of scenes, mostly due to, for example, the radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$.

  Another thing to remember is that while it is shown to be integrated over a sphere, it is almost always, and will be for the rest of this document, integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  Unfortunately, this formula does not work very well in regards to bidirectional path tracing. The reason is because BDPT requires to work in terms of surfaces rather than solid angle, ei, $v_0 \rightarrow v_1$. So now the rendering equation must be transformed from solid angle to surfaces:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. In terms of SDFs, the surface
    is every point on an SDF map where $|map| \leq \epsilon$. There's no longer
    any integration over a hemisphere with solid angle $\omega_i$, it's now over
    every single surface in the scene. This will be explained in detail later.
\\
    In the case of $L_e$,
    DTOADQ [at least, for now], only has support for area-light. Thus consider:

@@

    The cos term, used for the projected solid angle in irradiance, no longer
    applies when dealing with area. This and $d\omega_i$ now become a
    generalized geometry term, G, that converts a PDF with respect to solid area
    using Jacobian mapping, which involves the inverse squared distance, and the
    cosine angle between the geometric normals at $v$ and $\dot{v}$:

@@

    Where $V$ is the visibility test. Thus the rendering equation with respects
    to area is:
  \begin{align}
    L(v \rightarrow \dot{v}) = L_e(v \rightarrow \dot{v}) \int_ML(v \rightarrow
    \dot{v}) G(v\leftrightarrow \dot{v}) f_s(v\rightarrow \dot{v} \rightarrow
    \ddot{v}) d_A
  \end{align}
    where $A$ is the area on $M$, and $M$ is the union of all scene surfaces.
    This is known as the three-point form or the light transport equation. By
    recursively expanding$^{[1]}$, so that the three point form is integrated
    over every possible set of possible paths, this can be rewritten as the more
    usable format:
  \begin{align} I_j = \int_\Omega f_j(\bar{v}) d\mu(\bar{v}) \end{align}
    Where $\bar{v}$ is a path $z_0\rightarrow z_s \rightarrow y_t \rightarrow
    y_0 (eye \rightarrow light)$, $\Omega$ is the combination of all possible
    paths of any length, and $\mu$ is the area-product measure [the product of
    all the expanded $d_A$]. Special care has to be taken with the definition of
    path itself, as in the source code, there never exists a path $\bar{v}$,
    only eye-path $\bar{z}$ and light-path . Right now, this is analytically
    unsolvable. To compute this, we need to apply monte carlo sampling and limit
    the maximum path length:
  \begin{align}
    I_j \approx \frac{1.0f}{N}\Sigma_0^NF\\
    F = \Sigma_s\Sigma_t\frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})}
  \end{align}

    where $s$ is the light-path length, and $t$ is the eye-path length. In
    DTOADQ, they are limited to $s+t \leq 8$[TODO]. Finally, to transform
    $\bar{v}$ into two seperate paths, $\frac{f_j(\bar{v}_{s,
        t})}{p(\bar{v}_{s, t})}$ is split into two with a connection edge $c$
  \begin{align}
    \frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})} \equiv
    \frac{f^L(\bar{y})}{p(\bar{y})} c(\bar{y}_s \leftrightarrow \bar{z}_t)
    \frac{f^E(\bar{z})}{p(\bar{z})}  
  \end{align}

    And now
  \begin{align}
    F = \Sigma_s\Sigma_t \alpha^L_s c_{s, t} \alpha^E_t
  \end{align}
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      \frac{L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | \frac{W^0_e(z_0)}{p_A(z_0)},
      &i = 1,\\
      (\frac{f_s(y_{i+1} \rightarrow y_i \rightarrow y_{i-1})}{p_{\sigma}(y_i
      \rightarrow y_{i-1})} | \frac{f_s(z_{i-1} \rightarrow z_{i-2} \rightarrow
      z_{i-3}}{p_\sigma(z_{i-2} \rightarrow z_{i-1})}) \alpha^{L|E}_{i-1},
      &i > 1
    \end{cases}
  \end{align}
    There is no case for $i = 0$ as either, the path doesn't exist, or if one
    does exist, $y_0$ and $z_0$ do not contribute to the image. Veach (and many other
    sources), leave this in, but it's unnecessarily confusing. A special case
    needs to be handled, unfortunately, for $\alpha^E_0$ as it is being
    generated on the fly while $\bar{z}$ is being constructed. The two options
    is to unroll the first iteration of the construction loop, or just allow the
    special case to exist. The latter is the better choice, as all kernels will
    enter and exit the special case at the same time, and the GPU might just
    unroll the loop anyways.
    There may be cases where $s = 0$ ($t = 0$ is not possible without a
    physical camera lens), which is equivalent to just forward path tracing.
    There is also to consider, what happens on $s = 1$ and $t = 1$, %TODO
    Well, in either case where both paths exist or only the camera path exists,
    the connection strategy below describes how to connect the edges of the two
    paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 1,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s > 0, t > 1
    \end{cases}
  \end{align}
    Is the $s = 0, t > 1$
    strategy worthwhile to compute? Those familiar with next event
    estimation would know that there are situations in which this is beneficial.
    Take, for example, a glossy surface with a small solid angle subtending to
    the surface of a large light source. The $s=1$ sample strategy in this case
    would only contribute when the $L0$ vertex is within that solid angle.
    The effective strategy to sample in this case is $s = 0$.
    In code, $\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

@@

    One immediately obvious optimization that could be made with this model is
    in regards to the visibility check in the geometric term, if you were to
    expand $I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be
    cancelled out for the entire equation, except for the connection term $c$.
    This is intuitive as the paths
    $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ had just been generated via raymarching.
    Specifically, the definition of $V$ is
  \begin{align}
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
  \end{align}
    where $m$ is a march through the SDF map. A visibility check is only
    necessary for the connection edge
    \begin{align*}
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 
    \end{align*}
\\
    Moving on, for $\alpha^{L|E}_i$, these are equivalent for both $L$ and $E$,
    the problem is that the $\bar{y}$ path is generated in perspective of the
    light source, so there has to be a bit of caution in terms of perspective in when generating the PDFs.

     $p_A$ is
    the PDF w.r.t. area, for the light path; we only need to take the PDF of the
    solid angle of a sphere
  \begin{align}
    p_A^L(y_0 \rightarrow y_1) = p_{\sigma}^L(y_0 \rightarrow y_1) G(v
    \leftrightarrow \dot{v})\\
    p_{\sigma}^L(y_0 \rightarrow y_1) = \frac{1.0f}{\tau * (1.0f -
    \sqrt{\frac{R^2}{|y_0 - y_1|^2}})}
  \end{align}
    where $R$ is the radius of the sphere, note $y_0$ is a point on the surface
    of the sphere, and not its origin.
    \\$p_A^E(x_0 \rightarrow x_1)$ doesn't exist, as there is no physical lens
    on the scene. [TODO - this might cahnge later]. One of the benefits of this,
    is that there are no special cases for pathes where $t = 0$, which is
    impossible to handle on the GPU as the path could contribute to any
    arbitrary pixel [directly hitting the lens].
  \begin{align}
    P_A^E = 1.0f
  \end{align}
    The $L^0_e$ is contribution from the light source. As of right now, DTOADQ
    only supports area lights, so $L^0_e$ is set a constant for the emitter's
    spectrum value.
    The $W_e^0$ is contribution from the eye source, that is, the lens. Since
    the lens does not exist in the scene, as of now [TODO - this might change
    later], there is no $W_e^0$. While this should be implemented in the future,
    a hidden benefit of the current model is that there are no special cases for
    paths where $t = 0$, which is impossible to handle on the GPU as any such
    path could contribute to any arbitrary pixel [the light path is, after all,
    directly hitting the lens]. So this has now become:
  \begin{align}
    \alpha_i^E = \Sigma_{i\leq 0} 
  \end{align}
  The amount that each path contributes to F differ greatly, so naively
  weighing each contribution uniformly by something like 1.0f, or even, by
  inverse path length, will producy very noisy images, and would not be
  worth the additional computation time that BDPT requires, as shown below.
  	 To calculate the PDF of 
  In order to get good
  samples from the contributions, they must be combined in an optimal manner
  using Multiple Importance Sampling: each contribution is weighted by the PDF
  of the entire path itself:
  \begin{align*}
    F &\equiv \Sigma_s\Sigma_tW_{s, t}C_{s, t}\\
    C_{s, t} &= \alpha^L_s c_{s, t} \alpha^E_t
  \end{align*}
    where $W_{s, t}$ is the MIS weight of path $\bar{y} \leftarrow \bar{z}$, and
    $C_{s, t}$ is the unweighted contribution of the same path. For clarity,
    $C^U_{s, t}$ as described below is the unweighted contribution of the
    algorithm:
  \begin{align}
    C^u_{s, t} = (\alpha^L_s c_{s, t} \alpha^E_t) \equiv
    \frac{f_j(\bar{v})}{p(\bar{v})}
  \end{align}
  thus
  \begin{align}
    F = \Sigma_s\Sigma_tW_{s, t}C^u_{s, t}
  \end{align}
    The formula for Multiple Importance Sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
    generated, while the denominator is the path density of other connection
    strategies that could could have, in theory,$^{[1]}$ created the path. The
    straight forward implementation of this has a lot of problems gone
    unresolved in Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses
    and describe these problems. Primarily, $P_i(\bar{x})$ will overflow
    CLFloat (due to the distance in the Geometric term), and the straight
    forward implementation is very long, hard to debug, and has a poor time
    complexity. But the important part is the end result of their solution:

  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}

    However, DTOADQ can simplify a bit further; unlike above, there are two
    paths for which to evaluate. Specifically, in the above term, for where
    $i < s$, we have
    $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$, 
    which is the light path (i is iterating towards light-length s). The eye
    contribution is inversed from this, (also iterating towards s, hence why
    $\bar{x}_{i-1}$ is used). Another way of saying it, is $\bar{x} = \bar{y} ||
    \bar{z}_{rev}$.
    In DTOADQ's case, the weights are calculated in
    the same direction relative to its originator; in this case the perspective
    of the eye path.
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And then the expanded form of $\mathcal{W}_i(\bar{x})$ looks like

>>>>

\message{ !name(test.tex)}\documentclass{article}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[margin=1.15in]{geometry}
\author{aodq}

@@

  	It seems that the GPU is not for me or DTOADQ and something I do not enjoy
to use nor am good at. However, for this project, I had to deal with it. To
overcome the lack of a random function, of which high quality uniform random
generation is necessary for Monte Carlo simulations, I used the MWC64X
algorithm. While there are better algorithms, they fail on branches which makes
it useless for DTOADQ. It seemed to work well enough. The downside is that each
worker/pixel needs its own random state, preserved across multiple kernel calls.
There are indefinitely better solutions.
  \section{Light Transport Introduction}
  \section{Bidirectional Path Tracing}
    The main foundation of the mathematics and theory have come from many
sources, such as Veach's thesis to PBR 3rd ed. and various open source path
tracing kernels such as NanoRT, Embree, etc. However, the implementation differs
from these in that the algorithm is optimized for the GPU. This section is about
transforming the algorithms and mathematical models into something easily and
efficiently implementable the GPU, however I will work from the ground up in the
theory and mathematics behind light transport.

@@

  Now, the importance of probability distribution functions comes when
performing Monte Carlo approximation on an integral. Take, for instance, the
most well-known form of the rendering equation:
  \begin{align}
    L_o(P, \omega_o) = L_e(P, \omega_o) + \int_{S}f_s(P, \omega_i,
    \omega_o) L_i(P, \omega_i) \vert cos\theta_i\vert d\omega_i
  \end{align}

  Where:
  \begin{list}{}{}
  	 \item $Lo(P,\:\omega_o)$ is the radiance at point $P$ in space towards direction $\omega_o$.

  	 \item $L_e(P,\:\omega_o)$ is the emittance at point $P$ towards $\omega_o$
      (such as a lamp).

  	 \item $S$ is the unit sphere in which the angle $\omega_i$ is integrated
        over in respects to the normal at $P$. Also, this means, implicitly,
        that the equation is in respects to solid angle; the angle at which a
        primitive $A$ subtends $B$.

  	 \item $f_s$ is the Bidirectional Scattering Distribution Function. This
        will be detailed in the BSDF chapter, suffice it to say, it describes
        how photons are scattered (or absorbed) from point P in space from
        direction $\omega_i$ towards $\omega_o$ -- either through reflection
        (BRDF), or transmittance (BTDF). In volumetric path tracing, there is
        also subsurface scattering, but this phenomena is only approximated in
        DTQ.

  	 \item $L_i(P, \omega_i)$ is the rendering equation at P from $\omega_i$

  	 \item And $cos\theta_i$ is the normal attenuation.
  \end{list}
  Conceptually, this is the behavior of photons bouncing off several surfaces of
a scene. While it's a very simple model, it's impossible to solve analytically
for anything but the most simple of scenes, mostly due to, for example, the
radiance at $P0$ relies on $P1$, and $P1$ relies on $P0$. Another thing to
remember is that while it is shown to be integrated over a sphere, it is usually
shown to be integrated over hemisphere $\Omega$ using either $f_r$ or $f_s$.

  To compute this unbiasedly, it is required to use PDFs as described before to
approximate the integral using Monte Carlo simulation. The technique is to
generate $N$ uniformly random samples, weight them by their probability
distribution, and then average the results:

  \begin{align}
   \int{f(x)} \: \approx \frac{1}{N}\Sigma_0^N{\frac{f(x)}{p(x)}}
  \end{align}

  With standard "backward" path tracing, a photon would be emitted from a light
source and scatter in the scene until it hit an 'eye' or 'camera'. While this is
what happens in reality, in computer graphics, most of the samples never end up
hitting the camera/eye, so it is much more efficient to instead start from the
eye, and end at an emitter/light source. In this case, since we are integrating
over solid angle, the probably distribution function would be related to
sampling the BRDF. So for example, on a specular surface, the PDF is $1.0$ where
$\omega_o = reflect(\omega_i, N)$ and $0.0$ otherwise. An obvious optimization
is to only sample over the valid BSDF angles, which is known as importance
sampling. In DTQ, there are three BSDF functions:

  \begin{list}{}{}
  \item BSDF Spectrum: The albedo at $(P,\:\omega_i,\:\omega_o)$
  \item BSDF Sample: Samples a $\omega_o$ given $(P,\:\omega_i)$
  \item BSDF PDF: The probability distribution of $(P,\:\omega_i,\:\omega_o)$
  \end{list}

  There are many more optimizations to be made as well. For example, at each
scattering event, an additional photon can be sent towards each emitter. This is
what is known as next-event estimation. While this improves performance
drastically, naively averaging each contribution is incorrect, because each path
has a different probability to their paths/contributions. The technique to
sample them properly, multiple importance sampling, is related to BDPT, however
it will be detailed . The important thing to understand is that, in this
sampling strategy, there is a new PDF introduced which relates to the
probability of a path being generated, and this is critical to understand the
concept of BDPT.

  Now, the optimization that is of focus in DTQ is Bidirectional Path Tracing.
Instead of starting from an eye or light, a 'photon' (path) is generated from
both, allowed to scatter in the scene for a few paths (the length is determined
by Russian Roulette), and connected. It's not exactly the end-points of the
paths that are being connected, but each vertex generated is connected to each
other. [SHOW EXAMPLE]. This actually has an interesting correlation to
next-event estimation, as it could be seen as 'extending' the amount of emitters
that can be connected to.

  For BDPT, like a lot of different light transport equations, things go much
more smoothly when the equation uses a different measure. In this case, the
measure is over surface area rather than solid angles. This looks like $v_0
\rightarrow v_1$. The transformation looks like so:
  \begin{align}
    f_s(v \rightarrow \dot{v} \rightarrow \ddot{v}) &= f_s(P, \omega_i,
                                                      \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e(P, \omega_o)\\
    L_e(v \rightarrow \dot{v}) &= L_e^0(v) L_e^1(v \rightarrow \dot{v})
  \end{align}
    That is, instead of looking at a point $P$ with an incoming and outgoing
    angle $(\omega_i,\:\omega_o)$, look at the path from $P_{-1}$ ($v$) to
    $P_{+1}$ ($\ddot{v}$). More accurately, it's the transport between
    three different surfaces of the scene. There's a small change to be made in
the case of $L_e$, as DTOADQ [at least, for now], only has support for
area-light. Thus consider:

@@

    The $cos\theta_i$ is no longer applicable, instead there is now a geometry
term, G, that converts a PDF with respect to solid angle to surface area, which
involves the inverse squared distance, and the cosine angle between the
geometric normals at $v$ and $\dot{v}$:

@@

    Where $V$ is the visibility test. Thus the rendering equation with respects
    to area is:
  \begin{align}
    L(v \rightarrow \dot{v}) = L_e(v \rightarrow \dot{v}) \int_ML(v \rightarrow
    \dot{v}) G(v\leftrightarrow \dot{v}) f_s(v\rightarrow \dot{v} \rightarrow
    \ddot{v}) d_A
  \end{align}
    where $A$ is the area-measurement function on $M$, and $M$ is the set of all
points on the surface of a scene. That is, to say in regards to SDFs, $M$ is the
set of all points $P$ where $|map(P)| < \epsilon$. The area-measurement function
goes into measure theory, which while it is beyond my grasp currently to
compute, conceptually I understand a bit of it. The important thing is that $A$
is a function on the set of all subsets of $M$ that returns the measurement of
each set, and as long as the surfaces of the scene are sampled uniformly, this
never actually has to be computed. To back it up a little further, Veach
presented this as a means to integrate over a measure rather than using solid
angles. This proves that you can transform the rendering equation to different
measurements. For example, instead of integrating over points on surfaces, one
could integrate over an entire 3D space in order to perform volumetric path
tracing. Transforming the rendering equation using measurements would be
interesting in the future to look into.

    Anyways, with the three-point form now described, by recursively expanding,
so that the three point form is integrated over every possible set of possible
paths, this can be rewritten as the more usable format:
  \begin{align} I_j = \int_\Omega f_j(\bar{v}) d\mu(\bar{v}) \end{align}
    Where $\bar{v}$ is a path $z_0\rightarrow z_s \rightarrow y_t \rightarrow
    y_0 (eye \rightarrow light)$, $\Omega$ is the combination of all possible
    paths of any length, and $\mu$ is the area-product measure [the product of
all the expanded $A$]. Special care has to be taken with the definition of
    path itself, as in the source code, there never exists a path $\bar{v}$,
    only eye-path $\bar{z}$ and light-path . Monte Carlo approximation, as shown
above, is applied to the formula:
  \begin{align}
    I_j \approx \frac{1.0f}{N}\Sigma_0^NF\\
    F = \Sigma_s\Sigma_t\frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})}
  \end{align}

    where $s$ is the light-path length, and $t$ is the eye-path length. In
    DTOADQ, they are limited to $s+t \leq DEPTH$, a kernel-defined macro.
Finally, to transform $\bar{v}$ into two seperate paths, so that an eye and
light path may be generated, $\frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})}$ is
split into two with a connection edge $c$
  \begin{align}
    \frac{f_j(\bar{v}_{s, t})}{p(\bar{v}_{s, t})} \equiv
    \frac{f^L(\bar{y})}{p(\bar{y})} c(\bar{y}_s \leftrightarrow \bar{z}_t)
    \frac{f^E(\bar{z})}{p(\bar{z})}  
  \end{align}

    And now
  \begin{align}
    F = \Sigma_s\Sigma_t \alpha^L_s c_{s, t} \alpha^E_t
  \end{align}

  $\alpha_{s|t}^{L|E}$ is the final radiance of either the emitter or eye path,
  and thus it is recursive in nature. That is, the value of $\alpha_i$ is
  dependent on $\alpha_{i-1}$, unless $i = 0$ in which case is the radiance of
  either the emitter or the eye path. This is shown below.
  \begin{align}
    \alpha^{L|E}_i =
    \begin{cases}
      \frac{L_e^0(y_0 \rightarrow y_1)}{p_A(y_1)} | \frac{W^0_e(z_0)}{p_A(z_0)},
      &i = 1,\\
      (\frac{f_s(y_{i+1} \rightarrow y_i \rightarrow y_{i-1})}{p_{\sigma}(y_i
      \rightarrow y_{i-1})} | \frac{f_s(z_{i-1} \rightarrow z_{i-2} \rightarrow
      z_{i-3}}{p_\sigma(z_{i-2} \rightarrow z_{i-1})}) \alpha^{L|E}_{i-1},
      &i > 1
    \end{cases}
  \end{align}
    For the case of $i = 0$, this would mean that the path does not exist. In
other words, forward or backward path tracing, the latter of which isn't
supported as camera lens are not defined in DTQ. Veach (and many other sources),
leave this in, but it's unnecessarily confusing. For $i = 1$, it is either a
point on the surface of a light, or the origin point on the 'delta eye'. The
connection strategy below describes how to connect the edges of the two paths
  \begin{align}
    c_{s, t} =
    \begin{cases}
      L_e(z_{-2} \rightarrow z_{-1}), &s = 0, t > 1,\\
      f_s(y_{-2} \rightarrow y_{-1} \rightarrow z_{-1}) G(y_{-1} \leftrightarrow
      z_{-1}) f_s(y_{-1} \rightarrow z_{-1} \rightarrow z_{-2}), &s > 0, t > 1
    \end{cases}
  \end{align}
    Is the $s = 0, t > 1$ strategy worthwhile to compute? Those familiar with
next event estimation would know that there are situations in which this is
beneficial. Take, for example, a glossy surface with a small solid angle
subtending to the surface of a large light source. The $s=1$ sample strategy in
this case would only contribute when the $L0$ vertex is within that solid angle.
The effective strategy to sample in this case is $s = 0$. In code,
$\alpha_i^E\:c_{s,t}\:\alpha_0^L$ looks like (MIS not shown):
    \begin{lstlisting}
     float3 wi = normalize(E1.origin - E0.origin),
            wo = normalize(L1.origin - E1.origin);
     float3 albedo = _BRDF_F(wi, E1.normal, wo, E1.material, E1.mat_col);
     albedo /= BSDF_PDF(wo, wi, &E1);
     Spectrum contribution = E1.radiance * albedo;
     contribution *= Geometric_Term(&E1, &L1, si, Tx);
     contribution *= tlight.emission/Light_PDF(&tlight);
    \end{lstlisting}

@@

    One immediately obvious optimization that could be made with this model is
in regards to the visibility check in the geometric term, if you were to expand
$I_j$, and take the V term from outside the G function
    [$G(v \rightarrow
    \dot{v}) V(v \rightarrow \dot{v})$],
    it would be made obvious that all the visibility checks can be cancelled out
for the entire equation, except for the connection term $c$. This is intuitive
as the paths $\bar{y}_{0} \ldots \bar{y}_s$ and $\bar{z}_0 \ldots \bar{z}_t$ had
just been generated via raymarching. Specifically, the definition of $V$ is
  \begin{align}
    V(v \rightarrow \dot{v}) = ||v - \dot{v}|| \leq
    m(v,\:\overrightarrow{v\:\dot{v}})
  \end{align}
    where $m$ is a march through the SDF map. A visibility check is only
necessary for the connection edge
    \begin{align*}
      ||v - \dot{v}|| = m(v, \overrightarrow{v, \dot{v}})\\
      \:\:\:\text{for all paths but } y_{-1} \rightarrow z_{-1} 
    \end{align*}
\\
    Moving on, for $\alpha^{L|E}_i$, these are equivalent for both $L$ and $E$,
the problem is that the $\bar{y}$ path is generated in perspective of the light
source, so there has to be a bit of caution in terms of perspective in when
generating the PDFs. $p_A$ is the PDF w.r.t. area, for the light path; we only
need to take the PDF of the solid angle of a sphere
  \begin{align}
    p_A^L(y_0 \rightarrow y_1) = p_{\sigma}^L(y_0 \rightarrow y_1) G(v
    \leftrightarrow \dot{v})\\
    p_{\sigma}^L(y_0 \rightarrow y_1) = \frac{1.0f}{\tau * (1.0f -
    \sqrt{\frac{R^2}{|y_0 - y_1|^2}})}
  \end{align}
    where $R$ is the radius of the sphere, note $y_0$ is a point on the surface
of the sphere, and not its origin. \\$p_A^E(x_0 \rightarrow x_1)$ doesn't exist,
as there is no physical lens on the scene. [TODO - this might cahnge later]. One
of the benefits of this, is that there are no special cases for pathes where $t
= 0$, which is impossible to handle on the GPU as the path could contribute to
any arbitrary pixel [directly hitting the lens].
  \begin{align}
    P_A^E = 1.0f
  \end{align}
    The $L^0_e$ is contribution from the light source. As of right now, DTOADQ
only supports area lights, so $L^0_e$ is set a constant for the emitter's
spectrum value. The $W_e^0$ is contribution from the eye source, that is, the
lens. Since the lens does not exist in the scene, as of now [TODO - this might
change later], there is no $W_e^0$. While this should be implemented in the
future, a hidden benefit of the current model is that there are no special cases
for paths where $t = 0$, which is impossible to handle on the GPU as any such
path could contribute to any arbitrary pixel [the light path is, after all,
directly hitting the lens]. So this has now become:
  \begin{align}
    \alpha_i^E = \Sigma_{i\leq 0} 
  \end{align}
  The amount that each path contributes to F differ greatly, so naively weighing
each contribution uniformly by something like 1.0f, or even, by inverse path
length, will producy very noisy images, and would not be worth the additional
computation time that BDPT requires, as shown below. To calculate the PDF of In
order to get good samples from the contributions, they must be combined in an
optimal manner using Multiple Importance Sampling: each contribution is weighted
by the PDF of the entire path itself:
  \begin{align*}
    F &\equiv \Sigma_s\Sigma_tW_{s, t}C_{s, t}\\
    C_{s, t} &= \alpha^L_s c_{s, t} \alpha^E_t
  \end{align*}
    where $W_{s, t}$ is the MIS weight of path $\bar{y} \leftarrow \bar{z}$, and
$C_{s, t}$ is the unweighted contribution of the same path. For clarity,
$C^U_{s, t}$ as described below is the unweighted contribution of the
    algorithm:
  \begin{align}
    C^u_{s, t} = (\alpha^L_s c_{s, t} \alpha^E_t) \equiv
    \frac{f_j(\bar{v})}{p(\bar{v})}
  \end{align}
  thus
  \begin{align}
    F = \Sigma_s\Sigma_tW_{s, t}C^u_{s, t}
  \end{align}
    The formula for Multiple Importance Sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
generated, while the denominator is the path density of other connection
strategies that could could have, in theory,$^{[1]}$ created the path. The
straight forward implementation of this has a lot of problems gone unresolved in
Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses and describe these
problems. Primarily, $P_i(\bar{x})$ will overflow CLFloat (due to the distance
in the Geometric term), and the straight forward implementation is very long,
hard to debug, and has a poor time complexity. But the important part is the end
result of their solution:
  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}
    However, DTOADQ can simplify a bit further; unlike above, there are two
paths for which to evaluate. Specifically, in the above term, for where $i < s$,
we have $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$,
which is the light path (i is iterating towards light-length s). The eye
contribution is inversed from this, (also iterating towards s, hence why
$\bar{x}_{i-1}$ is used). Another way of saying it, is $\bar{x} = \bar{y} ||
\bar{z}_{rev}$. In DTOADQ's case, the weights are calculated in the same
direction relative to its originator; in this case the perspective of the eye
path.
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And then the expanded form of $\mathcal{W}_i(\bar{x})$ looks like
  \begin{align}
    \mathcal{W}_i(\bar{x}) = \Pi_{n=2}^i(\frac{\overleftarrow
    {p_{\sigma}}(x_n)\overleftarrow {G}(x_n)}
    {\overrightarrow{p_{\sigma}}(x_n)\overrightarrow{G}(x_n)})
    * \frac{\overleftarrow{p_A}(x_1)}{\overrightarrow{p_A}(x_1)}
  \end{align}
    And now the MIS looks like:
  \begin{align}
    MIS_{s, t}(\bar{y}, \bar{z}) =
    \frac{1.0f}{\mathcal{W}_s(\bar{y}) + \mathcal{W}_t(\bar{z}) + 1.0f}
  \end{align}
